Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-06-23 latex/refs.tex
changing paper and makin slides

\section{Reviewer 2}
\subsection{Measurement Clusterization vs Repetition}
I will start by saying measurement clusterisation is not well-defined
in this paper. On page 1, it is referred to as two sets of
measurements that are almost indistinguishable from one
another. However, the setup for Corollary 11 implicitly defines
measurement clusterisation as repeated measurements. The latter
definition matches the references of Fedorov (1996) and Nyberg et al
(2012). So I will assume for the rest of this review that, measurement
clusterisation refers to repeated measurements.  Nearly all textbooks
on classical design of experiments (e.g. Morris, 2011, Section 1.2.4)
will feature a section with the three words randomisation, blocking
and repetition: the important principles of design of experiments.  In
these texts, repeated measurements are considered to be a beneficial
property of a design. Interestingly, when optimal designs are found,
they are often found to have repeated measurements.  The paper does
not explain why the author thinks repeated measurements (measurement
clusterisation) is an undesirable property. If one looks at, for
example, Fedorov (1996) and Nyberg et al (2012), it is an undesirable
property because they are interested in sensor location, and two or
more sensors cannot be in the same location. However, there are many
experiments where repeated measurements are possible, and are
therefore optimal (if the model is correct, which it won’t be). An
example, is a chemical engineering experiment where one wishes to
learn the relationship between a series of variables and yield of a
chemical reaction. The experiment will involve specifying the
variables, and measuring the yield (the observation) after a specified
period of time. This process is then duplicated with a potentially
different set of variables.  It is perfectly possible to have repeated
variables.
\begin{enumerate}
\item The author needs to make clear that they are considering
  experiments where repeated measurements are impossible. Admitedly,
  this consideration is implicit in the paper, for example, the
  examples given on page 1. However, it needs to be made explicit in
  the Abstract and the first paragraph of the paper.

@@

\item Experiment with the 1D heat equation: the experiment showcases
  some interesting phenom- ena, but also raises many questions. For
  instance: I would expect the dimensionality of the working domain
  (here the unit interval [0, 1]) to play a role, since larger
  dimension allow for higher freedom in placing the design points.

\item Further, a dimensionality effect should also arise directly from
  Theorem 1 via the prior co- variance eigenvalues: in the experiment
  the prior covariance operator is set to be equal to the inverse
  Laplace operator $(−\Delta)^{−1}$ . In d-dimensional domains, its
  eigenvalues λj are known to follow Weyl’s asymptotics, growing as j
  2/d , which should then impact the index after which the eigenvalues
  are ‘thresholded’ by the procedure.

@@

>>>>

\section{Reviewer 2}
\subsection{Measurement Clusterization vs Repetition}
I will start by saying measurement clusterisation is not well-defined
in this paper. On page 1, it is referred to as two sets of
measurements that are almost indistinguishable from one
another. However, the setup for Corollary 11 implicitly defines
measurement clusterisation as repeated measurements. The latter
definition matches the references of Fedorov (1996) and Nyberg et al
(2012). So I will assume for the rest of this review that, measurement
clusterisation refers to repeated measurements.

Nearly all textbooks on classical design of experiments (e.g. Morris,
2011, Section 1.2.4) will feature a section with the three words
randomisation, blocking and repetition: the important principles of
design of experiments.  In these texts, repeated measurements are
considered to be a beneficial property of a design. Interestingly,
when optimal designs are found, they are often found to have repeated
measurements.  The paper does not explain why the author thinks
repeated measurements (measurement clusterisation) is an undesirable
property. If one looks at, for example, Fedorov (1996) and Nyberg et
al (2012), it is an undesirable property because they are interested
in sensor location, and two or more sensors cannot be in the same
location. However, there are many experiments where repeated
measurements are possible, and are therefore optimal (if the model is
correct, which it won’t be). An example, is a chemical engineering
experiment where one wishes to learn the relationship between a series
of variables and yield of a chemical reaction. The experiment will
involve specifying the variables, and measuring the yield (the
observation) after a specified period of time. This process is then
duplicated with a potentially different set of variables.  It is
perfectly possible to have repeated variables.

\begin{enumerate}

\item The author needs to make clear that they are considering
  experiments where repeated measurements are impossible. Admitedly,
  this consideration is implicit in the paper, for example, the
  examples given on page 1. However, it needs to be made explicit in
  the Abstract and the first paragraph of the paper.

@@

  Answer: It is impossible to visually discern the measurements, even
  when resolution is increased.

\item Experiment with the 1D heat equation: the experiment showcases
  some interesting phenomena, but also raises many questions. For
  instance: I would expect the dimensionality of the working domain
  (here the unit interval [0, 1]) to play a role, since larger
  dimension allow for higher freedom in placing the design points.

  Answer: That is a great point! I added the followng discussion:

\item Further, a dimensionality effect should also arise directly from
  Theorem 1 via the prior covariance eigenvalues: in the experiment
  the prior covariance operator is set to be equal to the inverse
  Laplace operator $(−\Delta)^{−1}$ . In d-dimensional domains, its
  eigenvalues $\lambda_j$ are known to follow Weyl’s asymptotics,
  growing as $j^{2/d}$, which should then impact the index after
  which the eigenvalues are ‘thresholded’ by the procedure.

@@

Answer: Thanks for this comment but I would rather keep this section
here since...
